IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/proofs.tex
safe space in proof.

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us the right-hand side of the implication in the TSNI
  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$.
    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
    where |lcurr| is the label of |it1|.
    In this case, we do not need to take a step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1| (can be seen
    by inspecting all reduction rules), they will get filtered
    by |erasef il| in |ic1'|.  Therefore, the |il|-equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to |iS1|:
    Only three reduction interact with |iS1|,
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label |il'| gets added to the message
      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task |it1| can change, which gets erased.
    \end{description}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
    %    \alphacondition{We need all scheduling policies to not change the order
    %      of any tasks (except for the first one).  Newly spawned task can appear
    %      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.
    Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il|-equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list.
    This is the case regardless of any additional side conditions $P$ on
    rules, because for all of these tasks, it can either take an actual
    step, or it gets dropped by \textsc{I-noStep} (which is always
    possible, as there cannot be an additional side condition on this
    rule).  All tasks that didn't get dropped are still at a label
    that isn't below |il| and thus get erased.

>>>>

\begin{proof}[Proof of Theorem~\ref{thm:iso-tsni}]
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case,
  we split the derivation sequence from~\eqref{eq:tsni-lhs} of length $n+1$ as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general} to
  the first step and
  the induction hypothesis to the rest of the derivation sequence,
  we directly get the desired property.
  % long version
%  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
%  The base case for derivations
%  of length 0 is trivial, allowing
%  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
%  the theorem holds for derivation sequences of length up to $n$, and show that it also
%  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
%  \[
%  |ic1| |.->| |ic1''| |.->|^n |ic1'|
%  \]
%  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
%  |ic''| with
%  \begin{equation} \label{eq:tsni-proof-1}
%  |ic1''| \approx_{|il|} |ic2''|
%  \qquad \text{and} \qquad
%  |ic2| |.->|^* |ic2''|
%  \end{equation}
%  Applying the induction hypothesis to
%  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
%  \begin{equation} \label{eq:tsni-proof-2}
%  |ic1'| \approx_{|il|} |ic2'|
%  \qquad \text{and} \qquad
%  |ic2''| |.->|^* |ic2'|
%  \end{equation}
%  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
%  us the right-hand side of the implication in the TSNI
%  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$.
    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
    where |lcurr| is the label of |it1|.
    In this case, we do not need to take a step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1| (can be seen
    by inspecting all reduction rules), they will get filtered
    by |erasef il| in |ic1'|.  Therefore, the |il|-equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to |iS1|:
    Only three reduction interact with |iS1|,
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label |il'| gets added to the message
      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task |it1| can change, which gets erased.
    \end{description}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
    %    \alphacondition{We need all scheduling policies to not change the order
    %      of any tasks (except for the first one).  Newly spawned task can appear
    %      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.
    Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il|-equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list.
    This is the case regardless of any additional side conditions $P$ on
    rules, because for all of these tasks, it can either take an actual
    step, or it gets dropped by \textsc{I-noStep} (which is always
    possible, as there cannot be an additional side condition on this
    rule).  All tasks that didn't get dropped are still at a label
    that isn't below |il| and thus get erased.
